\section*{Author contributions}
%-------------------------------------------------------------------------------------------------------------

% Viktor
\textcolor{olive}{Viktor Eriksson researched stated topics to verify the information in the report. Additional literature for missing supported information.
Engaged in sampling methodology for both EMG and EEG such as testing, discussing, and conducting conclusions. Been mainly involved in practical setups.}

% Carl
\textcolor{violet}{Carl Larsson wrote first draft of Abstract, Introduction, Method, Results, Discussion, Conclussion and all tables and equations. Conducted thorough research and investigation of literature for finding state of the art and methods for this study. Thorough review and identification of improvements for this report and study. Implementation of all statistical tests and all code for processing. Ensured the report followed IEEE standards. Leadership role.}

% Pontus
\textcolor{teal}{Pontus Svensson conducted extensive literature reasearch, focusing on state-of-the-art methods. Engaged in discussions with group members to determine the projects direction and identify areas for improvement. Implemented all code for running in real-time, and implemented communication protocol to the \href{https://github.com/ROBOTIS-GIT/turtlebot3}{Turtlebot3} using \href{https://docs.ros.org/en/humble/index.html}{ROS2}. Implemented protocol for sampling EMG and EEG signals.}

%-------------------------------------------------------------------------------------------------------------


%-------------------------------------------------------------------------------------------------------------
\begin{comment}
    all text in the report should be color-coded for each author.
\end{comment}
%-------------------------------------------------------------------------------------------------------------